---
title: "Demand Forecasting - BS1808 Logistics and Supply Chain Analytics - Store 46673"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
<br />
<br />



##################################################################STORE 46673###################################################################


###descritive###



```{r}
#loading the data for store 46673
store46673 = read.csv('46673.csv', header = TRUE)
```

```{r}
#make the importded data time series data (frequency=7 as weekly time intervals make it easier to read the data)
ts_store46673 <- ts(store46673[,'total_lettuce'], frequency = 7)
```


```{r}
#plotting the time series data
plot.ts(ts_store46673, main='Store 46673: Lettuce Demand 13/03/2015-15/06/2015', xlab='Weeks', ylab='Lettuce Demand per Day in Ounces', col = 'blue')
```

```{r}
#show histogram of the time series data to assess skewness/distribution
hist(ts_store46673, main = 'Store 46673: Historgam of Lettuce Demand per Day', xlab='Lettuce Demand per Day in Ounces')
```


```{r}
boxplot(ts_store46673, main = "Store 46673:Boxplot of Lettuce Demand per Day")
```
```{r}
#summary statistics of the time series data
summary(ts_store46673)
```

```{r}
#standard deviation of the time series data
sd(ts_store46673)
```

```{r}
#skewness of the time series data
moments:::skewness(ts_store46673)
```

```{r}
#kurtosis of the time series data
moments:::kurtosis(ts_store46673)
```

###decomposition of original time series###

```{r}
ts_store46673_dec <- stl(ts_store46673, s.window ='periodic' , s.degree = 0) 
plot(ts_store46673_dec, main = 'Store 46673: Decomposition of Time Series')
```

###Holt-Winters###

```{r}
# Application of Holt Winters Function
ts_store46673_HW <- HoltWinters(ts_store46673, beta = FALSE) 
ts_store46673_HW
```
alpha = level smoothing
beta = trend smoothing
gamma = seasonal smoothing

```{r}
#In-Sample Error of the Holt Winters Model
sqrt(ts_store46673_HW$SSE/(length(ts_store46673)-2)) 
```


```{r}
#ETS Function Application
ts_store46673_ETS <- forecast:::ets(ts_store46673, model = "ZZZ")
ts_store46673_ETS 
```


```{r}
# In-Sample error ETS
accuracy(ts_store46673_ETS)
```



```{r}
# In-Sample Performance of Holt Winters and ETS
plot(ts_store46673_HW, main='Holt-Winters and ETS In-Sample Comparison', xlab='Weeks', ylab='Lettuce Demand per Day in Ounces', col = 'black')
lines(fitted(ts_store46673_ETS), col = 'yellow')
legend('bottomright', legend=c('Original','HW', 'ETS'), col=c('black', 'red', 'yellow'), lty=c(1,1,1))
```

```{r}
# to more reliably assess the accuracy of ETS and Holt Winter we need an out of sample error. Therefore, it makes sense to split the available data into a training and a validation data set (75%, 25%)
```

```{r}
# training data
ts_store46673_T<- ts(store46673[1:(nrow(store46673)*0.80),'total_lettuce'], frequency = 7)
ts_store46673_T
```

```{r}
# validation data
 ts_store46673_V <- store46673[(nrow(store46673)*0.8+1):nrow(store46673),'total_lettuce']
 ts_store46673_V
```

```{r}
# Holts winter forecast with splitted data
ts_store46673_HW_T <- HoltWinters(ts_store46673_T, beta = FALSE) 
ts_store46673_HW_F <- forecast:::forecast.HoltWinters(ts_store46673_HW_T, h = 20)
ts_store46673_HW_F 
```

```{r}
# Holt Winter Forecast Splitted Data
plot(ts_store46673_HW_F, main = 'Store 46673: Holt Winters Forecast with Splitted Data', xlab='Time', ylab='Lettuce Demand per Day in Ounces', col = 'black') 
lines(fitted(ts_store46673_HW_F), col = "skyblue3") 
legend('bottomright', legend=c('True','Forecasted values', 'Fitted values'), col=c('black', 'skyblue3', 'blue'), lty=c(1,1,1))
```


```{r}
#accuracy of the Holt Winters soplitted data forecast
accuracy(ts_store46673_HW_F, ts_store46673_V) 
```


```{r}
# ETS forecast with splitted data
ts_store46673_ETS_T <- ets(ts_store46673_T)
ts_store46673_ETS_F <- forecast.ets(ts_store46673_ETS_T, h = 20)
```

```{r}
# ETS Forecast Splitted Data
plot(ts_store46673_ETS_F, main = 'Store 46673: ETS Forecast with Splitted Data', xlab='Time', ylab='Lettuce Demand per Day in Ounces', col = 'black') 
lines(fitted(ts_store46673_ETS_F), col = "skyblue3") 
legend('bottomright', legend=c('True','Forecasted values', 'Fitted values'), col=c('black', 'skyblue3', 'blue'), lty=c(1,1,1))
```

```{r}
#accuracy of the ETS splitted data forecast
accuracy(ts_store46673_ETS_F, ts_store46673_V) 
```


```{r}
# Train Model for 14 days Holt Winters Forecast
ts_store46673_ETS_Forecast <- forecast.ets(ts_store46673_ETS, h = 14)
ts_store46673_ETS_Forecast
```

```{r}
#ETS Forecast
plot(ts_store46673_ETS_Forecast, main = 'ETS Forecast', xlab='Time', ylab='Lettuce Demand per Day in Ounces', lty = 1, col = "black")
lines(fitted(ts_store46673_ETS_Forecast), col = 'skyblue3') 
legend('bottomright', legend=c('True values','Forecasted values', 'Fitted values'), col=c('black', 'skyblue3', 'blue'), lty=c(1,1,1))
```
```{r}
plot(acf(ts_store46673_ETS_Forecast$residuals,main = 'ETS Forecast', lag.max=20), main = 'ACF of ETS') 
```


```{r}
plot.ts(ts_store46673_ETS_Forecast$residuals, main='ETS Forecast Error over time', xlab='Time', ylab='Residuals', col = 'darkblue')
```


```{r}
# Ljung-Box Test to check whether the error is independently distributed
Box.test(ts_store46673_ETS_Forecast$residuals, lag=20, type='Ljung-Box')
```
 Null Hypothesis: indendetly distributed data
 p-value sufficently large => not rejecting the null hypothesis and therefore assume independence of the error term
```{r}
# Argumented Dickey Fuller Test to check whether data is stationary
tseries::adf.test(ts_store46673_ETS_Forecast$residuals)
```
 Null Hypothesis: non-stationary
 p-value< 0.05 => reject the null hypothesis at a significance level of 5% => stationary
 
 
```{r}
#Box-Pierce to check whether data is autocorrelated
Box.test(ts_store46673_ETS_Forecast, type='Box-Pierce')
```
 Null Hypothesis: zero autocorrelation
 p-value sufficently large => not rejecting the null hypothesis => no autocorrelation
 
 
 ###ARIMA###
 
 
 ###testing (stationarity, iid, autocorrelation)###

```{r}
# Ljung-Box Test to check whether data is independently distributed
Box.test(ts_store46673, type='Ljung-Box')
```
 Null Hypothesis: indendetly distributed data
 p-value very small => rejection of null hypothesis and therefore assume dependence
 
```{r}
# Argumented Dickey Fuller Test to check whether data is stationary
tseries::adf.test(ts_store46673)
```
 Null Hypothesis: non-stationary
 p-value smaller than printed p-value => reject the null hypothesis => stationary
```{r}
#KPSS test for level of stationarity
kpss.test(ts_store46673)
```

```{r}
#Box-Pierce to check whether data is autocorrelated
Box.test(ts_store46673, type='Box-Pierce')
```
 Null Hypothesis: zero autocorrelation
 p-value very small => reject the null hypothesis => autocorrelation
 
```{r}
#Philips-Perron Test to check order/existence of autocorrelation
tseries:::pp.test(ts_store46673)
```
 Null Hypothesis: non-stationary
 p-value smaller than printed p-value => reject the null hypothesis => stationary

```{r}
#number of first order differences in order to make the time series stationary
forecast:::ndiffs(ts_store46673)
```
```{r}
#number of seasonal difference in order to make the time series stationary
forecast:::nsdiffs(ts_store46673)
```
 
```{r}
install.packages('forecast')
library(forecast)
```
 
```{r}
#first seasonal difference 
ts_store46673_1D <- diff(ts_store46673, differences = 1, lag = 7)
plot.ts(ts_store46673_1D)
```

 
```{r}
# ACF of original time series
ggAcf(ts_store46673, main = 'Store 46673: ACF of the Original Time Series Daily')
```

```{r}
ggPacf(ts_store46673, main = 'Store 46673: PACF of the Original Time Series Daily')
```







```{r}
# ACF of first differenced time series
plot(acf(ts_store46673 , lag.max = 200), main = 'Store 46673: ACF of the First Differenced Time Series Weekly') 
```

```{r}
# PACF of first differenced time series
plot(pacf(ts_store46673 , lag.max = 200), main = 'Store 46673: ACF of the First Differenced Time Series Weekly') 
```
 
 

```{r}
#AFC of seasonal difference time series daily
ggAcf(ts_store46673_1D, main = 'Store 46673: ACF of the Seasonal Differenced Time Series Daily')
```

```{r}
#ACF of the seasonal differnced time series weekly
plot(acf(ts_store46673_1D , lag.max = 200), main = 'Store 46673: ACF of the Seasonal Differenced Time Series Weekly') 
```

```{r}
#PACF of the seasonal differened time series daily 
ggPacf(ts_store46673_1D, main = 'Store 46673: PACF of the Seasonal Differenced Time Series Daily')
```
 
```{r}
#PACF of the seasonal differnced time series weekly
plot(pacf(ts_store46673_1D , lag.max = 200), main = 'Store 46673: PACF of the Seasonal Differenced Time Series Weekly') 
```

```{r}
#auto ARIMA
forecast:::auto.arima(ts_store46673, trace = TRUE, ic = 'bic', approximation = FALSE)
```
 
```{r}
#Fitting training data set on ARIMA option 1 
ts_store46673_ARIMA1_T <- Arima(ts_store46673_T, order = c(0, 0, 0),seasonal = list(order = c(2, 1, 0), period = 7)) 
```
 
```{r}
#Forecasting training data set for ARIMA option 1
ts_store46673_ARIMA1_T_F<- forecast:::forecast.Arima(ts_store46673_ARIMA1_T, h = 20)
```

```{r}
# Accuracy Forecasting training data set for ARIMA option 1
forecast:::accuracy(ts_store46673_ARIMA1_T_F, ts_store46673_V) 
```

 
```{r}
#Fitting training data set on ARIMA option 2 
ts_store46673_ARIMA2_T <- Arima(ts_store46673_T, order = c(0, 0, 1),seasonal = list(order = c(2, 1, 0), period = 7))
```
 
```{r}
#Forecasting training data set for ARIMA option 2
ts_store46673_ARIMA2_T_F<- forecast:::forecast.Arima(ts_store46673_ARIMA2_T, h = 20)
```


```{r}
# Accuracy Forecasting training data set for ARIMA option 2
forecast:::accuracy(ts_store46673_ARIMA2_T_F, ts_store46673_V) 
```

 
```{r}
#Fitting training data set on ARIMA option 3
ts_store46673_ARIMA3_T<- Arima(ts_store46673_T, order = c(1, 0, 0),seasonal = list(order = c(2, 1, 0), period = 7))
```
 
 
```{r}
#Forecasting training data set for ARIMA option 3
ts_store46673_ARIMA3_T_F<- forecast:::forecast.Arima(ts_store46673_ARIMA3_T, h = 20)
```
 
```{r}
# Accuracy Forecasting training data set for ARIMA option 3
forecast:::accuracy(ts_store46673_ARIMA3_T_F, ts_store46673_V) 
```

 
```{r}
#complete 14 days forecast with ARIMA1
ts_store46673_ARIMA1_C <- Arima(ts_store46673, order = c(1, 0, 0),seasonal = list(order = c(2, 1, 0), period = 7))
ts_store46673_ARIMA1_CF<- forecast:::forecast.Arima(ts_store46673_ARIMA1_C, h = 14)
ts_store46673_ARIMA1_CF
```

```{r}
accuracy(ts_store46673_ARIMA1_C)
```


```{r}
#plotting complete 14 day ARIMA1 forecast
#ETS Forecast
plot(ts_store46673_ARIMA1_CF, main = 'ARMIA(1,0,0)(2,1,0)(7) Forecast', xlab='Time', ylab='Lettuce Demand per Day in Ounces', lty = 1, col = "black")
lines(fitted(ts_store46673_ARIMA1_CF), col = 'skyblue3') 
legend('bottomright', legend=c('True values','Forecasted values', 'Fitted values'), col=c('black', 'skyblue3', 'blue'), lty=c(1,1,1))

```
```{r}
plot(acf(ts_store46673_ARIMA1_CF$residuals,main = 'Autocorrelation of ARIMA (0,0,1)(2,1,0)(7) Residuals ', lag.max=20)) 
```
 



```{r}
plot.ts(ts_store46673_ARIMA1_CF$residuals, main=' ARMIA(0,0,1)(2,1,0)(7) Forecast Error over time', xlab='Time', ylab='Residuals', col = 'darkblue')
```
 
```{r}
# Ljung-Box Test to check whether the error is independently distributed
Box.test(ts_store46673_ARIMA1_CF$residuals, lag=20, type='Ljung-Box')
```


```{r}
# Argumented Dickey Fuller Test to check whether data is stationary
tseries::adf.test(ts_store46673_ARIMA1_CF$residuals)
```




```{r}
#Box-Pierce to check whether data is autocorrelated
Box.test(ts_store46673_ARIMA1_CF$residuals, type='Box-Pierce')
```


```{r}
#conductiong the final 14 days forecast
store46673_RESULTS <- forecast.ets(ts_store46673_ETS, h = 14)
store46673_RESULTS 
```

```{r}
#save the results as CSV
write.csv(store46673_RESULTS, 'store46673_RESULTS.csv')
```

 